Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-19 Ch1_movement_rates/Ch1_Figures.Rmd
YEs! we have figure 4
Ok, almost finished with the figures for ch1.

# Color palette ----------------------------------------
my.cols1 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")

@@

qtable_models
```

@@

points_plot <- function(seed.data, summ.data, s.size = 5000, xylims=1250, lalpha = 0.5, scenario = NULL, twoplots = FALSE){

@@

disp_df %>%
  group_by(., model) %>%
  sample_n(., 5000) %>%
  #mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  #scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
  labs(y = "Dispersion in meters") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  sample_n(., 5000) %>%
  #mutate(dispcat = ifelse(av.disp <500, "non", "ldd")) %>%
  ggplot(., aes(y = av.disp, x = model
                #, color = dispcat
                )) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
  labs(y = "Average dispersal in meters") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) -> p_dispersal

@@

```{r fig.height=9}
plot_grid(seedplots2d, disp2_plot, nrow = 2)

@@

```{r}
cp.df %>% 
  drop_na(s.id) %>% 
  left_join(., cp.summ.df) -> testdata

testdata %>% 
  sample_n(1000) %>% 
  ggplot(., aes(x = xloc, y = yloc, color = dsprsn)) +
  geom_point() +
  scale_color_viridis_c(direction = -1) +
  theme_bw()

cp.summ.df %>% 
  sample_n(1000) %>% 
  ggplot(., aes(y = dsprsn, x = av.disp)) +
  geom_point()

cp.summ.df %>% 
  sample_n(100) %>% 
  ggplot(., aes(x = x, y = y, color = dsprsn)) +
  scale_color_gradient(low = "green", high = "blue") +
  geom_point(alpha = 0.8) +
  coord_equal() +
  theme_bw()

@@

joint_weib %>% 
  mutate(model = factor(model, levels = c("cp", "pp",
                                          "np"))) -> joint_weib

@@

```{r}
joint_weib %>%
  group_by(model) %>%
  sample_n(., 200) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  geom_hline(aes(yintercept = 1), lty = "dashed") +
  labs(title = "Shape") +
  #scale_y_continuous(limits = c(0, 2)) +
  theme_bw() -> weib_shape

joint_weib %>%
  group_by(model) %>%
  sample_n(., 200) %>%
  ggplot(., aes(x = model, y = est.scale)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Scale") +
  theme_bw() -> weib_scale

@@

```{r}
library(kde1d)

@@

@@

plot(cp.shape.kde$grid_points, cp.shape.kde$values, type="l", lwd=2, bty="l", col="red", ylim = c(0,4))
lines(pp.shape.kde$grid_points, pp.shape.kde$values, col="blue")
lines(np.shape.kde$grid_points, np.shape.kde$values, col="black")

plot(cp.scale.kde$grid_points, cp.scale.kde$values, type="l", lwd=2, bty="l", col="red", ylim = c(0,0.04))
lines(pp.scale.kde$grid_points, pp.scale.kde$values, col="blue")
lines(np.scale.kde$grid_points, np.scale.kde$values, col="black")

>>>>

# Color palette ----------------------------------------
my.cols1 <- c("#23262f","#717492","#b3a82a","#c94f21","#980012","#0d907a","#b9bec3")
scales::show_col(my.cols1)

@@

knitr::kable(qtable_models)
```

@@

points_plot <- function(seed.data, summ.data, s.size = 50000, xylims=1250, lalpha = 0.5, scenario = NULL, twoplots = FALSE){

@@

disp_df %>%
  group_by(., model) %>%
  sample_n(., 10000) %>%
  #mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  #scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
  labs(y = "Dispersion in meters") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  sample_n(., 10000) %>%
  #mutate(dispcat = ifelse(av.disp <500, "non", "ldd")) %>%
  ggplot(., aes(y = av.disp, x = model
                #, color = dispcat
                )) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
  labs(y = "Average dispersal in meters") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) -> p_dispersal

@@

```{r fig.height=7.5, fig.width=9}
plot_grid(seedplots2d, disp2_plot, nrow = 2)

@@

@@

joint_weib %>% 
  mutate(model = toupper(model),
         model = factor(model, levels = c("CP", "PP","NP"))) -> joint_weib

@@

The violin plot here is made with all the data, the jitter points are a random sample of 200

```{r}
joint_weib %>%
  group_by(model) %>%
  #sample_n(., 100) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(data = joint_weib %>% 
                group_by(model) %>% 
                sample_n(200),
              position = position_jitter(0.1)) +
  geom_hline(aes(yintercept = 1), lty = "dashed") +
  labs(y = "Shape") +
  #scale_y_continuous(limits = c(0, 2)) +
  theme_bw() +
  theme(axis.title.x = element_blank()) +
  NULL -> weib_shape

joint_weib %>%
  group_by(model) %>%
  #sample_n(., 200) %>%
  ggplot(., aes(x = model, y = est.scale)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(data = joint_weib %>% 
                group_by(model) %>% 
                sample_n(200),
              position = position_jitter(0.1)) +
  labs(y = "Scale") +
  theme_bw() +
  theme(axis.title.x = element_blank()) +
  NULL-> weib_scale

@@

Kernel density estimation plots with kde1d

```{r fig.width=9, fig.height=3.5}
library(kde1d)

@@

rbind(CIs.cp.shape, CIs.pp.shape, CIs.np.shape, CIs.cp.scale, CIs.pp.scale, CIs.np.scale) %>% 
  as.data.frame() %>% 
  rename(low = V1, mean = V2, high = V3) %>%
  tibble::rownames_to_column("model") %>% 
  mutate(param = stringr::str_sub(model, start = 8),
         model =stringr::str_sub(model, start = 5, end = 6),
         model = toupper(model),
         model = factor(model, levels = c("CP", "PP", "NP"))) -> CIdata

CIdata %>% 
  filter(., param == "shape") %>% 
  ggplot(., aes(x  = model, y = mean)) +
  geom_point() +
  geom_segment(aes(y = low, yend = high, x = model, xend = model)) +
  labs(y = "Value", x = "Shape") +
  #scale_color_manual(values = my.cols1[c(1,4,6)]) +
  theme_bw() +
  theme(legend.title = element_blank(),
        legend.position = c(0.9, 0.2)) -> ShapeCI

CIdata %>% 
  filter(., param == "scale") %>% 
  ggplot(., aes(x  = model, y = mean)) +
  geom_point() +
  geom_segment(aes(y = low, yend = high, x = model, xend = model)) +
  labs(y = "Value", x = "Scale") +
  #scale_color_manual(values = my.cols1[c(1,4,6)]) +
  theme_bw() +
  theme(legend.title = element_blank(),
        legend.position = c(0.9, 0.2)) -> ScaleCI

plot_grid(ShapeCI, ScaleCI)

@@

```{r fig.width=9}
data.frame(grid_points = cp.shape.kde$grid_points, values = cp.shape.kde$values, model = "CP", param = "shape") %>% 
  bind_rows(., data.frame(grid_points = pp.shape.kde$grid_points, values = pp.shape.kde$values, model = "PP", param = "shape")) %>% 
  bind_rows(., data.frame(grid_points = np.shape.kde$grid_points, values = np.shape.kde$values, model = "NP", param = "shape")) %>% 
  bind_rows(., data.frame(grid_points = cp.scale.kde$grid_points, values = cp.scale.kde$values, model = "CP", param = "scale") %>% 
  bind_rows(., data.frame(grid_points = pp.scale.kde$grid_points, values = pp.scale.kde$values, model = "PP", param = "scale")) %>% 
  bind_rows(., data.frame(grid_points = np.scale.kde$grid_points, values = np.scale.kde$values, model = "NP", param = "scale"))) %>% 
  mutate(model = factor(model, levels = c("CP", "PP", "NP"))) -> kerneldata

kerneldata %>% 
  filter(., param == "shape") %>% 
  ggplot(., aes(x = grid_points, y = values, color = model)) +
  geom_line() +
  labs(y = "Density", x = "Shape") +
  scale_color_manual(values = my.cols1[c(1,4,6)]) +
  theme_bw() +
  theme(legend.title = element_blank(),
        legend.position = c(0.9, 0.2)) -> shapeplot

kerneldata %>% 
  filter(., param == "scale") %>% 
  ggplot(., aes(x = grid_points, y = values, color = model)) +
  geom_line() +
  labs(y = "Density", x = "Scale") +
  scale_color_manual(values = my.cols1[c(1,4,6)]) +
  theme_bw() +
  theme(legend.title = element_blank(),
        legend.position = c(0.9, 0.2)) -> scaleplot

plot_grid(shapeplot, scaleplot, ncol = 2)

# plot(cp.shape.kde$grid_points, cp.shape.kde$values, type="l", lwd=2, bty="l", col="red", ylim = c(0,4))
# lines(pp.shape.kde$grid_points, pp.shape.kde$values, col="blue")
# lines(np.shape.kde$grid_points, np.shape.kde$values, col="black")
# 
# plot(cp.scale.kde$grid_points, cp.scale.kde$values, type="l", lwd=2, bty="l", col="red", ylim = c(0,0.04))
# lines(pp.scale.kde$grid_points, pp.scale.kde$values, col="blue")
# lines(np.scale.kde$grid_points, np.scale.kde$values, col="black")
